\documentclass{article}%
\usepackage[T1]{fontenc}%
\usepackage[utf8]{inputenc}%
\usepackage{lmodern}%
\usepackage{textcomp}%
\usepackage{lastpage}%
%
\title{Doc{-}It: AI{-}Generated Code Documentation}%
\author{Your Name}%
\date{\today}%
%
\begin{document}%
\normalsize%
\maketitle%
\section{Codebase Overview}%
\label{sec:CodebaseOverview}%
A codebase!\newline%
\newline%
As an expert software architect, my task is to analyze this entire codebase and provide a high{-}level summary of the project.\newline%
\newline%
**Project Overview**\newline%
\newline%
The project appears to be a tool for generating documentation and summaries from source code. It utilizes natural language processing (NLL) techniques to generate human{-}readable explanations of code changes. The tool is designed to work with various programming languages, including Python, JavaScript, HTML, CSS, and Markdown.\newline%
\newline%
**Key Features**\newline%
\newline%
1. **Codebase Summary**: The project can generate a high{-}level summary of the entire codebase, providing an overview of the project's purpose, technologies used, and overall structure.\newline%
2. **Change Explanation**: The tool can explain individual changes made to specific files, providing context about the change, its purpose, and potential impact on the project.\newline%
3. **Ollama API Integration**: The project integrates with the Ollama API, a natural language processing platform, to generate human{-}readable explanations of code changes.\newline%
\newline%
**Architecture**\newline%
\newline%
The project's architecture appears to be modular, with several utilities providing functionality for:\newline%
\newline%
1. **Config Handler**: Handles configuration files and default settings.\newline%
2. **Diff Utility**: Compares snapshots of file contents and identifies added, modified, or deleted files.\newline%
3. **LLM Utility**: Utilizes the Ollama API to generate summaries and explanations.\newline%
4. **DB Utility**: Manages database interactions for storing snapshot data.\newline%
\newline%
**Key Components**\newline%
\newline%
1. **Snapshots Directory**: Stores timestamped JSON files containing snapshots of file contents.\newline%
2. **Codebase Content**: A single string containing the content of all relevant files.\newline%
\newline%
Overall, this project appears to be a promising tool for generating documentation and summaries from source code.

%
\end{document}